---
title: "Untitled"
author: "Rui Zhang"
date: "10/11/2019"
output:
  html_document:
    df_print: paged
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(gridExtra)
data <- read.csv("D:/Google Drive/Math/Data Mining/Project/modeling_data.csv", 
                 header=TRUE, na.strings=c(".", "NA", "", "?"))
data$Book_12Mo <- as.factor(data$Book_12Mo)
data$Recommend_GAT <- as.factor(data$Recommend_GAT)
data$TravelAgain <- as.factor(data$TravelAgain)
data$Groups_Interest <- as.factor(data$Groups_Interest)
```
# **1. Checking missing values**
```{r echo=FALSE, warning=FALSE}
options(width = 600)
sapply(data, function(df){sum(is.na(df)==TRUE)})
```

# **2. Histogram of each variable**  
## 1) *FY*: Fiscal Year that the trip was taken  
#### The data for *FY07* (10/1/2006 ~ 9/30/2007) is strange.  
#### **Key word**: Great recession Dec. 2007 ~ June 2009. US economy slowed down in 2006.  
#### From plot 2 we can see that each year, the percentage of repeat customer are almost same. 
```{r, echo=FALSE, fig.width = 12, fig.height = 5, fig.align = "center"}
# library(gridExtra)
ggplot(data, aes(FY)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(FY,Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(FY, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) ->p2

grid.arrange(p1, p2, ncol = 2)
```

## 2) *Tour_Season*
#### The data is strange. Low season has the most customer, and what is "LL"?    
```{r, echo = FALSE, fig.width = 12, fig.height = 5,fig.align="center"}
ggplot(data, aes(Tour_Season)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Tour_Season,Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Tour_Season, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) -> p2

grid.arrange(p1, p2, ncol = 2)
```

## 3) *Tour_Type*  
#### Most customers choose escorted tours. Custom tours has the lowest percentage of repeat customers. Walking tours has the highest percentage of repeat customers.
```{r, echo =FALSE, fig.width = 16, fig.height=5, fig.align ="center"}
ggplot(data, aes(Tour_Type)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Tour_Type,Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Tour_Type, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) -> p2

grid.arrange(p1, p2, ncol = 2)
```

## 4) *Main_Ext*: Indicates the type of the tour  
#### Only 28.6% customers made extension to the main tour. However, if the customer extened the tour, the customer is more likely to book a travel within in a year.
```{r, echo =FALSE, fig.width = 10, fig.height=5, fig.align ="center"}
  ggplot(data, aes(Main_Ext)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Main_Ext, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Main_Ext, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) -> p2

grid.arrange(p1, p2, ncol = 2)
```

## 5) *Tour_Days*(numeric)  
#### There is no obvious skew for the distribution of "Tour_Days".  
#### Percentage and days seems have linear relationship, but may need transformation.  
####       Plot 3 is after transformation.Seems there is a outlier at very left. Seems the customers who have more tour days, is more likely to become a repeat customer.
```{r, echo =FALSE, fig.width = 16, fig.height=9, fig.align ="center"}
ggplot(data, aes(Tour_Days)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) +
             scale_x_continuous(breaks = seq(0,25,by=1)) -> p1

prop <- data %>% group_by(Tour_Days, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n)) %>% filter(Book_12Mo ==1)
ggplot(prop, aes(x = Tour_Days, y = pct)) +
  geom_point(color="blue", size=3) +
  geom_smooth() +
  labs(y = "Percentage of Repeat Customers") -> p2

ggplot(prop, aes(x = log(Tour_Days), y = pct)) +
  geom_point(color="blue", size=3) -> p3

grid.arrange(p1, p2, p3,ncol = 2)
```

## 6) *Pax_Category*: Type of customer that went on this tour  
#### Most customers are individual customer. GC > IN > FF > GM
```{r, echo =FALSE, fig.width = 12, fig.height=4.5, fig.align ="center"}
ggplot(data, aes(Pax_Category)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Pax_Category, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Pax_Category, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) -> p2

grid.arrange(p1, p2,ncol = 2)
```

## 7) *Grp_Size_Cat*, *Grp_Size*  
#### There is a outlier, group size = 4 only has 3 observations.
```{r, echo =FALSE, fig.width = 14, fig.height=8, fig.align ="center"}
data$Grp_Size_Cat <- factor(data$Grp_Size_Cat, levels=c("Under 25","25 to 29","30 to 34",
                                                        "35 to 39","40 to 43","43 to 45"))
ggplot(data, aes(Grp_Size_Cat)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Grp_Size_Cat, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Grp_Size_Cat, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 4) -> p2

ggplot(data, aes(Grp_Size)) +
  geom_bar() -> p3

prop1 <- data %>% group_by(Grp_Size, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n)) %>% 
  filter(Book_12Mo ==1)
ggplot(prop1, aes(Grp_Size, pct)) +
  geom_point() +
  scale_x_continuous(breaks = seq(0,80,by=2)) -> p4

grid.arrange(p1, p2,p3,p4,ncol = 2)
```
```{r, echo=FALSE}
cor.test(prop1$Grp_Size, as.numeric(prop1$pct))
```

## 8) *Capacity*, *Grp_Size/Capacity*  
#### Should consider add an interaction term *Grp_Size/Capacity*.
```{r, echo =FALSE, fig.width = 12, fig.height=4.5, fig.align ="center"}
ggplot(data) +
  geom_bar(aes(Capacity)) -> p1

xx <- data[, names(data) %in% c("Grp_Size","Grp_Size_Cat","Capacity","Book_12Mo")]
xx <- xx %>% mutate(ratio = Grp_Size/Capacity)
xx$cat[xx$ratio>0.8] = 5
xx$cat[xx$ratio>0.6 & xx$ratio <= 0.8] = 4
xx$cat[xx$ratio>0.4 & xx$ratio <= 0.6] = 3
xx$cat[xx$ratio>0.2 & xx$ratio <= 0.4] = 2
xx$cat[xx$ratio>0 & xx$ratio <= 0.2] = 1
xx$cat <- as.factor(xx$cat)
prop <- xx %>% group_by(cat, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n)) %>% filter(Book_12Mo==1)
ggplot(prop) +
  geom_point(aes(cat,pct),color="blue",size=3) +
  scale_x_discrete(labels = c("20%","20~40%","40~60%", "60~80%","80~100%",">100%")) +
  labs(x="Grp_Size/Capacity", y = "Percentage of Repeat Customers") -> p2
grid.arrange(p1, p2,ncol = 2)
```

## 9) *Tour_Region*  
#### This variable has 18 missing values.  
#### *IT* is the most popular destination. Customers who go to *AF*, *AU*, *CNE*, *FS*, *MD* are more like to become repeat customers.
#### *CR* has the highest repeat customer rate, but the sample size is small.
```{r, echo =FALSE, fig.width = 14, fig.height=9, fig.align ="center"}
ggplot(data, aes(Tour_Region)) +
  geom_bar() +
  geom_text(stat='count',
            aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5,) -> p1

prop <- data %>% group_by(Tour_Region, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Tour_Region, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 3.5) -> p2
grid.arrange(p1, p2,nrow = 2)
```

## 10) *Recommend_GAT*, *TravelAgain*
#### As mentioned before, about 90% customers indicate that they will book tour within a year, and they will recommend the company to their friedn and family.  
#### "1" - NO, "2" - Yes, and I assume that "0" means the customers who didn't answer the question.  
#### What supersised me is the about 7~8% customers who answered "NO" book a trip within a year.
```{r, echo =FALSE, fig.width = 14, fig.height=4.5, fig.align ="center"}
prop <- data %>% group_by(Recommend_GAT, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Recommend_GAT, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 3.5) +
  scale_x_discrete(labels = c("0","NO","YES"))-> p1

prop <- data %>% group_by(TravelAgain, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(TravelAgain, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 3.5) + scale_x_discrete(labels = c("0","NO","YES")) -> p2
grid.arrange(p1, p2,ncol = 2)
```

## 11) *Groups_Interest*: Would you be interested in hearing more about our groups program  
```{r, echo =FALSE, fig.width = 14, fig.height=4.5, fig.align ="center"}
ggplot(data, aes(Groups_Interest)) +
  geom_bar()+
  geom_text(stat = 'count', aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5) +
  scale_x_discrete(labels = c("0","NO","YES")) -> p1

prop <- data %>% group_by(Groups_Interest, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Groups_Interest, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 3.5) + scale_x_discrete(labels = c("0","NO","YES")) -> p2
grid.arrange(p1, p2,ncol = 2)
```

## 12) *Reference*: May we use you as a reference for other travelers  
#### The customer who answers "NO" and "O" is less likely to book a travel again.
```{r, echo =FALSE, fig.width = 14, fig.height=4.5, fig.align ="center"}
ggplot(data, aes(Reference)) +
  geom_bar()+
  geom_text(stat = 'count', aes(label = scales::percent(prop.table(stat(count)))),vjust = -0.5) +
  scale_x_discrete(labels = c("0","NO","YES")) -> p1

prop <- data %>% group_by(Reference, Book_12Mo) %>% tally() %>% mutate(pct=n/sum(n))
ggplot(prop, aes(Reference, pct, fill=Book_12Mo)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 2) +
  geom_text(aes(label = scales::percent(pct)), vjust = 3.5) + scale_x_discrete(labels = c("0","NO","YES")) -> p2
grid.arrange(p1, p2,ncol = 2)
```
